ms2

### 2017-05-03 ms2/ms2.Rmd
streamlined

And for HRRs:

```{r}
left_join(hrr_abg, hrr_ineq, by=c('hrr', 'drug_group')) %>%
  left_join(hrr, by='hrr') %>%
  filter(bug=='E. coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region, size=sqrt(total))) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```

@@

## E.coli and penicillin

```{r}
ecoli_pen_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='penicillin') %>%
  filter(!is.na(mean_percent_nonsusceptible))

ecoli_bactrim_dat %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  #scale_x_continuous(limits=c(0.08, 0.2), breaks=c(0.08, 0.1, 0.15, 0.2)) +
  #ylim(10, 45) +
  #xlab('TMP/SMX claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```

>>>>

## E.coli and bactrim

@@

## Pneumococcus and macrolides

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='S. pneumoniae', drug_group=='macrolide') %>%
  filter(!is.na(mean_percent_nonsusceptible)) %>% 
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  theme_minimal()
```

## E. cloacae and quinolones

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Eb. cloacae', drug_group=='quinolone') %>%
  filter(!is.na(mean_percent_nonsusceptible)) %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  theme_minimal()
```
